Kang_02_nsc_Bscd
==================================================================================================================================
## Motivational Buckets
### 1) (size: 33) Jihun Kang's (2004) thesis titled "Valuing Flexibilities in Large-Scale Real Estate Development Projects" aims to develop a set of strategic tools for real estate development projects. TWO (2) methods are introduced to deal with the inadequecies of the Discounted Cash Flow (DCF) method: (a) Decision Tree Analysis (DTA); and (b) Real Options Analysis (ROA). This R Markdown file focused only on the latter method.
### 1.1) (size: 33) Most real estate development (RED), like Research and Development (RND) projects, do NOT make sense from the Net Present Value (NPV) standpoint. The most value of RED, like RND, is created when it becomes successful and opens up new market for a company. In other words, RED, like RND, is a right to acquire an exclusive and profitable market for the company at a cost incurred during the development, or research, process. Copeland and Weiner (1990) stated that the RED, like RND, situation is similar to "paying to see the next card" that provides the option to move forwards by investing more OR abandoning the project. Leslie and Michaels (1997) identified SIX (6) variables that can strategically improve the option value in a RED, or RND, project: (i) S - HIGHER underlying security price would give HIGHER option value. Like RND, it is difficult to observe the market price of an asset that does NOT produce an income stream. We could price S using TWO (2) methods: (a) cost less taxes; OR (b) DCF of expected net income stream. However, due to the uncertainty of the market we should not price S based on a random capital gain; (ii) X - as the strike price INCREASES, the value of a call option DECREASES. The strike price is equivalent to the present value (PV) of all the fixed costs expected over the lifetime of the development, or research, process; (iii) sigma - HIGHER volatility INCREASES the value of the option. This is a critical difference from the NPV approach. For highly risky projects, options strategy can dramatically improve their values. We could estimate sigma using TWO (2) approaches: (a) use a sigma constant for ALL REDs; OR (b) use a sigma based on country risk; (iv) T - as time to expiration INCREASES so does the value of an option; (v) c - dividends are considered as cost incurred to keep an option afloat. In RED, we used the loan interest rate as this is the financial cost of keeping the option afloat; and (vi) r - an expected INCREASE in the risk free rate RAISES option value. We could estimate risk free rate using TWO (2) methods: (a) opportunity cost for developing the real estate; OR (b) interest rate earned from a fixed deposit.

```{r}
if( Sys.info()["sysname"] == "Linux" )
  source("~/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE)
if( Sys.info()["sysname"] == "Windows" )
  source("C:/Users/denbrige/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE)
suppressPackageStartupMessages(source( paste0(RegGetRSourceDir(),"PlusBscd.R") ))
suppressPackageStartupMessages(require( fOptions ))
suppressPackageStartupMessages(require( testthat ))
sigma       <- 0.25
top.step    <- 12
top.year    <- 12
rf          <- 0.055
cc          <- 0.06
nsc.bscd    <- BscdCreateModel(rf, cc, top.step, top.year, sigma)
p.op        <- BscdOptionPrice(nsc.bscd, S=13562.513, X=2023.163, n=12, TypeFlag="ca")
p5.op       <- BscdOptionPrice(nsc.bscd, S=2361.567, X=3130.788, subMtx=p.op$ca, n=10, TypeFlag="ca")
p4.op       <- BscdOptionPrice(nsc.bscd, S=4274.987, X=4552.729, subMtx=p5.op$ca, n=8, TypeFlag="ca")
p3.op       <- BscdOptionPrice(nsc.bscd, S=1174.826, X=1308.519, subMtx=p4.op$ca, n=6, TypeFlag="ca")
p2.op       <- BscdOptionPrice(nsc.bscd, S=3260.798, X=2795.515, subMtx=p3.op$ca, n=4, TypeFlag="ca")
p1.op       <- BscdOptionPrice(nsc.bscd, S=1373.314, X=1203.098, subMtx=p2.op$ca, n=2, TypeFlag="ca")
```
### 1.1.1) (size: 19) The example above is taken from Kang's (2004) case study on "Valuing Flexibilities in the development of New Songdo City (NSC)". We reproduce the SIX(6)-stage sequential compound option for valuing NSC to demonstrate the use of Real Options Analysis (ROA) as a strategic tool. The FIVE (5) parameters used for the model and its assumptions are: (i) sigma=0.25 - HIGHER than the range for the US real estate market, and HIGHER than the volatility of the Korean housing index and Seoul's office survey as the properties in the entirely new city are likely to be more volatile in the beginning than the properties in mature cities; (ii) rf=0.055 - the SAME as rate of TEN(10)-year, the longest term, Korean government bond, since it matches quite well the duration of the project; (iii) c=0.06 - weighted AVERAGE of cap rates for ALL the properties in the project; (iv) T=12 - expected years to completion; (v) n=12 - the construction company would have an option to wait at least TWO (2) years before starting the next phase, therefore n=12,10,8... for Phase=6,5,4...
### 1.1.2) The FIRST option is for Phase SIX (P6) of the project: (a) S=1,117,022 - PV of benefits for P6; (b) X=2,023,163 - PV of costs for P6. The SECOND option is for Phase FIVE (P5) of the project: (a) S=2,361,567; (b) X=3,130,788. The THIRD option is for Phase FOUR (P4) of the project: (a) S=4,274,987; (b) X=4,552,729. The FOURTH option is for Phase THREE (P3) of the project: (a) S=1,174,826; (b) X=1,308,519. The FIFTH option is for Phase TWO (P2) of the project: (a) S=3,260,798; (b) X=2,795,515. Finally, the SIXTH option is for Phase ONE (P1) of the project: (a) S=1,373,314; (b) X=1,203,098. Note: ALL the options have TypeFlag="ca" and the PVs of benefits and costs are in US$ 1K. You need to sum the PVs of benefits and costs for EACH Phase in separate columns from Figure 6.10 (page 111). The net value created with the project is 1,113,928 (in thousands US$), which is the option price for P1 (1,370,478) LESS the PV of land cost for P1 (256,550) that was committed to purchase this option.

```{r fig.width=9, fig.height=6}
str(nsc.bscd)
BinomialTreePlot(p.op$ca)
BinomialTreePlot(p5.op$ca)
BinomialTreePlot(p4.op$ca)
BinomialTreePlot(p3.op$ca)
BinomialTreePlot(p2.op$ca)
BinomialTreePlot(p1.op$ca)
op.ca <- BinomialTreeOption("ca", S=13562.513, X=2023.163, Time=nsc.bscd$Time, r=nsc.bscd$r, b=nsc.bscd$b, sigma=nsc.bscd$sigma, n=nsc.bscd$n)
BinomialTreePlot(p.op$ca)
BinomialTreePlot(op.ca)
obs.op <- c(p.op$ca[1,1],
            p5.op$ca[1,1],
            p4.op$ca[1,1],
            p3.op$ca[1,1],
            p2.op$ca[1,1],
            p1.op$ca[1,1])
plot(seq(1,6,by=1), obs.op, col=seq(1:6),
     xlab="", ylab="Real Options Value (ROV in USD 1K)", main="Comparison of Phase SIX (6) to ONE (1) Options",
     pch=19)
legend(5.5, max(obs.op), c("P6","P5","P4","P3","P2","P1"), col=seq(1:6),
       pch=19)
text(seq(1,6,by=1)+0.1, obs.op, round(obs.op,1), col=seq(1:6))
```
### 1.1.3) (size: 33) The estimated sigma (0.25) is, to a large extent, a subjective estimate and thus it warrants a sensitivity analysis about this value. We show the result of option value sensitivity in relation to volatility (sigma) and asset value (S).
