Kang_01_real_options_Bscd
==================================================================================================================================
## Motivational Buckets
### 1) (size: 37) Jihun Kang's (2004) thesis titled "Valuing Flexibilities in Large-Scale Real Estate Development Projects" aims to develop a set of strategic tools for real estate development projects. TWO (2) methods are introduced to deal with the inadequecies of the Discounted Cash Flow (DCF) method: (a) Decision Tree Analysis (DTA); and (b) Real Options Analysis (ROA). This R Markdown file focused only on the latter method.
### 1.1) (size: 37) Most real estate development (RED), like Research and Development (RND) projects, do NOT make sense from the Net Present Value (NPV) standpoint. The most value of RED, like RND, is created when it becomes successful and opens up new market for a company. In other words, RED, like RND, is a right to acquire an exclusive and profitable market for the company at a cost incurred during the development, or research, process. Copeland and Weiner (1990) stated that the RED, like RND, situation is similar to "paying to see the next card" that provides the option to move forwards by investing more OR abandoning the project. Leslie and Michaels (1997) identified SIX (6) variables that can strategically improve the option value in a RED, or RND, project: (i) S - HIGHER underlying security price would give HIGHER option value. Like RND, it is difficult to observe the market price of an asset that does NOT produce an income stream. We could price S using TWO (2) methods: (a) cost less taxes; OR (b) DCF of expected net income stream. However, due to the uncertainty of the market we should not price S based on a random capital gain; (ii) X - as the strike price INCREASES, the value of a call option DECREASES. The strike price is equivalent to the present value (PV) of all the fixed costs expected over the lifetime of the development, or research, process; (iii) sigma - HIGHER volatility INCREASES the value of the option. This is a critical difference from the NPV approach. For highly risky projects, options strategy can dramatically improve their values. We could estimate sigma using TWO (2) approaches: (a) use a sigma constant for ALL REDs; OR (b) use a sigma based on country risk; (iv) T - as time to expiration INCREASES so does the value of an option; (v) c - dividends are considered as cost incurred to keep an option afloat. In RED, we used the loan interest rate as this is the financial cost of keeping the option afloat; and (vi) r - an expected INCREASE in the risk free rate RAISES option value. We could estimate risk free rate using TWO (2) methods: (a) opportunity cost for developing the real estate; OR (b) interest rate earned from a fixed deposit.

```{r}
if( Sys.info()["sysname"] == "Linux" )
  source("~/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE)
if( Sys.info()["sysname"] == "Windows" )
  source("C:/Users/denbrige/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE)
suppressPackageStartupMessages(source( paste0(RegGetRSourceDir(),"PlusBscd.R") ))
suppressPackageStartupMessages(require( stats ))
sigma       <- 0.2
top.month   <- 60
top.year    <- 5
rf          <- 0.03
aqua.bscd   <- BscdCreateModel(rf, 0, top.year, top.year, sigma)
bench.bscd  <- BscdCreateModel(rf, 0.09, top.year, top.year, sigma)
sell.gross  <- 6500/32.35
sell.net    <- sell.gross * 0.94
npv           <- function(ir, cf, t=seq(along=cf)) sum(cf/(1+ir)^t) 
irr           <- function(cf) { uniroot(npv, c(0,1), cf=cf)$root } 
aquaSpotNum   <- function(x) { x * 0.75 }
aquaEqualNum  <- function(x, ir, month) 
{ 
  equalNum  <- (x * 0.88)/month 
  equalVtr  <- rep(equalNum, month)
  npv(ir/12, equalVtr)
}
aquaDeferNum  <- function(x, ir, month)
{
  equalNum      <- (x * 0.4)/month
  equalVtr      <- rep(equalNum, month)
  equalVtr[month]  <- equalVtr[month] + (x * 0.6)
  npv(ir/12, equalVtr)
}
benchNum      <- function(x) { x * 0.75 }
sell.gross
aquaSpotNum(sell.gross)
aquaEqualNum(sell.gross, rf, top.month)
aquaDeferNum(sell.gross, rf, top.month)
benchNum(sell.gross)
aquaSpot.op   <- BscdOptionPrice( aqua.bscd, sell.net, aquaSpotNum(sell.gross) )
aquaEqual.op  <- BscdOptionPrice( aqua.bscd, sell.net, aquaEqualNum(sell.gross, rf, top.month) )
aquaDefer.op  <- BscdOptionPrice( aqua.bscd, sell.net, aquaDeferNum(sell.gross, rf, top.month) )
bench.op      <- BscdOptionPrice( bench.bscd, sell.net, benchNum(sell.gross) )
obs.op <- c(aquaSpot.op$ce[1,1],
            aquaEqual.op$ce[1,1],
            aquaDefer.op$ce[1,1],
            bench.op$ce[1,1])
```
### 1.1.1) (size: 37) Century Property provides THREE (3) financing options: (a) spot payment at 25% discount; (b) equal payment at 12% discount (up to 14%) over the lifetime of the development; and (c) 40-60 payment at 0% discount, where 40% of the purchase price is scheduled as equal payments over the lifetime of the development, and 60% of the purchase price is at the completion of the development (TOP). Depending on which option you choose, this will result in different fixed costs, i.e. X. Also, we used (d) a benchmark of borrowing the total amount of the fixed cost at c interest rate with spot payment at 25% discount. 
### 1.1.2) We valued the FOUR (4) options above while keeping the remaining FOUR (4) parameters of the Black-Scholes Discrete model constant: (i) S - selling price less 6% CGT, where selling price is assumed to be the listed purchase price; (ii) sigma - 0.2; (iii) T - 68/12; and (iv) r - 0.03;

```{r fig.width=9, fig.height=6}
plot(seq(1:4), obs.op, col=seq(1:4),
     xlab="", ylab="Real Option Value (ROV in SGD 1K)", main="Comparison of Financing Options",
     pch=19)
legend(3.5, max(obs.op), c("Spot","Equal","Defer","Bench"), col=seq(1:4),
       pch=19)
text(seq(1,4,by=1)+0.1, obs.op, round(obs.op,1), col=seq(1:4))

BscdSaMtx <- function(model, S, X, row.seq=seq(0.01, 0.2, by=0.01), col.seq=seq(1.0, 0.7, by=-0.05))
{
  sMtx <- matrix(0, nrow=length(row.seq), ncol=length(col.seq))
  for( vRow in seq_along(row.seq) )
  {
    sa.bscd <- BscdCreateModel(model$r, model$b, model$n, model$Time, row.seq[vRow])
    for( wCol in seq_along(col.seq) )
    {
      sa.op           <- BscdOptionPrice( sa.bscd, S*col.seq[wCol], X, TypeFlag="ce" )
      sMtx[vRow,wCol] <- sa.op$ce[1,1]
    }
  }
  sMtx
}
sMtx <- BscdSaMtx(aqua.bscd, S=sell.net, X=aquaEqualNum(sell.gross, rf, top.month))
round(sMtx,1)
```
### 1.1.3) The estimated sigma (0.2) is, to a large extent, a subjective estimate and thus it warrants a sensitivity analysis about this value. We show the result of option value sensitivity in relation to volatility (sigma) and asset value (S). For the SECOND option - equal payment - as asset value (net selling price) DECREASES from left (100%) to right (70%) column, the option price DECREASES. However, as volatility increases from top (1%) to bottom (20%) row, the option price INCREASES. The option price is positive for ALL parameters, except when asset value is LESS THAN EIGHTY FIVE (85%) and volatility is LESS THAN FIVE (5%) percent.
