Mt4r_03_Keiji_probot_tseries
==================================================================================================================================
## Motivational Buckets
### 1.1) (size: ) Keiji is the author of a script, namely "mt4to5rewrite_sample_v4_2.mq4", that converts MT4 code into MT5 code. This R Markdown file bases the main function on this script, in particular the start() function, but rather to convert MT4 to SqLite. 
### 1.2) (size: ) There are TWO (2) approaches to convert MT4 to SqLite: (a) replace ALL order tokens with the related SqLite tokens: (b) replace ANY command tokens - OrderSend, OrderModify, OrderClose, OrderDelete - with SqLite command arrays, if the command tokens are embedded within a query token - OrderSelect. In order to perform the latter approach, we MUST first build a knowledge data set of the existing code.
### 1.3) (size: ) There are SIX (6) internal functions: (i) FuncAddTop(); (ii) FuncAddInInit(); (iii) FuncAddInStart(); (iv) FuncAddInDeinit(); (v) FuncFind(); (vi) FuncRewrite().
### 1.4) (size: ) There are FIVE (5) include files: (i) "mt4accountinfo.mqh"; (ii) "mt4string.mqh"; (iii) "mt4datetime.mqh"; (iv) "mt4objects_1.mqh"; and (v) "mt4timeseries_2.mqh".
### 1.5) (size: ) We start with the end goal: (i) convert the mt.list (java) into mq4; (ii) add codes for include, init, deinit, and refresh (optionally comment); (iii) replace ALL order tokens with the related SqLite tokens; (iv) replace ANY command tokens with SqLite command arrays;

```{r}
if( Sys.info()["sysname"] == "Linux" )
  suppressPackageStartupMessages(source("~/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE))
if( Sys.info()["sysname"] == "Windows" )
  suppressPackageStartupMessages(source("C:/Users/denbrige/100 FxOption/103 FxOptionVerBack/080 Fx Git/R-source/PlusReg.R", echo=FALSE))
suppressPackageStartupMessages(source(paste0(RegRSourceDir(),"PlusFile.R"), echo=FALSE))
suppressPackageStartupMessages(source(paste0(RegRSourceDir(),"PlusMtr.R"), echo=FALSE))
suppressPackageStartupMessages(library(R.utils))
suppressPackageStartupMessages(library(tseries))
name.str  <- "Pro_Bot_EURUSD_m15_Risk"
java.str  <- MtrConvertStr(name.str)
if( file.exists(java.str) )
  mt.list <- lapply(readLines(paste0(java.str)), function(x) scan(text=x, sep=" ", 
                                                 what=c("char"), strip.white=c(FALSE)))
```
### 1.1.1) (size: ) In this instance, we "normalize" the Expert Advisor (EA) named "Pro_Bot_EURUSD_m15_Risk.mq4" into a java file "Pro_Bot_EURUSD_m15_Risk.java" by using the executable file "mq4_writer.exe". "Normalize" means to clean up and standardize the format of the code without changing its implementation. Ideally, we would have preferred to "normalize" the EA into a MQ4 file but there is no utility to perform this.
### 1.1.2) After the normalization process, we then read the java file into a list, where an element of the list corresponds to a line in the text file, and EACH element contains a vector of characters (including indentation).

```{r}
head(mt.list)
cmtDfr  <- MtrFindCmtDfr(mt.list)
cmtDfr
forDfr  <- MtrFindLoopDfr(mt.list, cmtDfr, tokenChr=c("for", "while", "do"))
forDfr
funDfr  <- MtrFindFunDfr(mt.list, cmtDfr)
funDfr  <- funDfr[funDfr$Name!="init", ]
funDfr  <- funDfr[funDfr$Name!="start", ]
funDfr  <- funDfr[funDfr$Name!="deinit", ]
funDfr
fubDfr  <- MtrBetweenFunDfr(mt.list, funDfr, cmtDfr)
fubDfr
fobDfr  <- MtrBetweenLoopDfr(mt.list, forDfr, cmtDfr, as.character(fubDfr$Name))
fobDfr
MtrAddTop <- function()
{
   return(list(c('//:::::::::::::::::::::::::::::::::::::::::::::'),
               c('#include','<PlusTurtle.mqh>'),
               c('#include','<PlusGhost.mqh>'),
               c('//:::::::::::::::::::::::::::::::::::::::::::::')));
}
MtrAddInInit <- function()
{
   return(list(c('//:::::::::::::::::::::::::::::::::::::::::::::'),
               c('TurtleInit();'),
               c('GhostInit();'),
               c('//:::::::::::::::::::::::::::::::::::::::::::::')));
}
MtrAddInDeinit <- function()
{
   return(list(c('//:::::::::::::::::::::::::::::::::::::::::::::'),
               c('GhostDeInit();'),
               c('//:::::::::::::::::::::::::::::::::::::::::::::')));
}
MtrAddInStart <- function()
{
   return(list(c('//:::::::::::::::::::::::::::::::::::::::::::::'),
               c('GhostRefresh();'),
               c('//:::::::::::::::::::::::::::::::::::::::::::::')));
}
MtrDeConvertStr <- function(name.str, mt.list, ea.dir=RegEaDir())
{
  
}
```

```{r}
sql.list <- list()
j <- 1
for( i in seq_along(mt.list) )
{
  #--- Read Line
  lineChr <- mt.list[[i]]
  
  #--- Account Query
  lineChr <- gsub("AccountFreeMargin", "GhostAccountFreeMargin", lineChr)
  
  #--- Sql Query  
  lineChr <- gsub("OrderTicket",      "GhostOrderTicket", lineChr)
  lineChr <- gsub("OrderSymbol",      "GhostOrderSymbol", lineChr)
  lineChr <- gsub("OrderOpenPrice",   "GhostOrderOpenPrice", lineChr)
  lineChr <- gsub("OrderMagicNumber", "GhostOrderMagicNumber", lineChr)
  lineChr <- gsub("OrderType",        "GhostOrderType", lineChr)
  lineChr <- gsub("OrderStopLoss",    "GhostOrderStopLoss", lineChr)
  lineChr <- gsub("OrderTakeProfit",  "GhostOrderTakeProfit", lineChr)
  
  #--- Sql Query with special cases
  lineChr <- gsub("OrderSelect", "GhostOrderSelect", lineChr)
  subBln  <- length(grep("GhostOrdersSelect", lineChr)) > 0
  posBln  <- length(grep("SELECT_BY_POS", lineChr)) > 0
  tktBln  <- length(grep("SELECT_BY_TICKET", lineChr)) > 0
  trdBln  <- length(grep("MODE_TRADES", lineChr)) > 0
  hsyBln  <- length(grep("MODE_HISTORY", lineChr)) > 0
  if( posBln & subBln )
  {
    
  }
  if( tktBln & subBln )
  {
    
  }  
  
  lineChr <- gsub("OrdersTotal", "GhostOrdersTotal", lineChr)
  subBln  <- length(grep("GhostOrdersTotal", lineChr)) > 0
  forBln  <- length(grep("for", lineChr)) > 0
  if( forBln & subBln )
  {
    #--- Prepend a line
    sql.list[[j]] <- c("int", "total", "=", "GhostOrdersTotal();")
    j <- j + 1
    lineChr <- gsub("GhostOrdersTotal\\(\\)", "total", lineChr)
  }
  
  #--- Sql Command
  lineChr <- gsub("OrderSend",   "GhostOrderSend", lineChr)
  lineChr <- gsub("OrderModify", "GhostOrderModify", lineChr)
  
  #--- Write Line
  sql.list[[j]] <- lineChr
  j <- j + 1
}
sql.list
```
### 1.3.1) (size: ) The internal function FuncRewrite() has an equivalent function gsub() in R.